### 2017-04-28 paper/jfp-submission/locating.tex
misc tweaks
tweak
minor

We compare \toolname's witness-based predictions against a baseline of
the \ocaml compiler as well as the state-of-the-art tools \sherrloc
and \mycroft.
%
\sherrloc attempts to predict the most likely source of a type error
by searching the typing constraint graph for constraints that participate
in many unsatisfiable paths and few satisfiable paths.
%
\mycroft reduces the localization problem to MaxSAT by searching for a
minimal subset of constraints that can be removed, such that the
resulting system is satisfiable.
%
Both tools produce a \emph{set} of equally-likely expressions to blame
for the error (in practice the set contains only a few expressions),
similar to \toolname's witness-based predictions.

We evaluate each tool based on whether \emph{any} of its predictions
identifies a changed expression.
%
There were a number of student programs where \mycroft or \sherrloc
encountered an unsupported language feature or timed out after one
minute, or where \toolname failed to produce a witness.
%
We discard all such programs in our evaluation to level the playing
field, leaving us with a benchmark set of 1,569 programs.

\begin{figure}[t]
\includegraphics[width=0.8\linewidth]{blame.png}
\caption{Accuracy of type error localization. \toolname's witness-based
  predictions outperform \ocaml by 22 points, and are competitive
  with the state-of-the-art tools \mycroft and \sherrloc.}
\label{fig:results-blame}
\end{figure}

>>>>

We compare \toolname's witness-based predictions against a baseline of
the \ocaml compiler as well as the state-of-the-art %type error
localization tools \sherrloc and \mycroft.
%
\sherrloc~\cite{Zhang2014-lv} attempts to predict the most likely source
of a type error by searching the typing constraint graph for constraints
that participate in many unsatisfiable paths and few satisfiable paths.
%
\mycroft~\cite{Loncaric2016-uk} reduces the localization problem to
MaxSAT by searching for a minimal subset of constraints that can be
removed, such that the resulting system is satisfiable.
%
Both tools produce a \emph{set} of equally-likely expressions to blame
for the error (in practice the set contains only a few expressions),
similar to \toolname's witness-based predictions.

We evaluate each tool based on whether \emph{any} of its predictions
identifies a changed expression.
%
There were a number of student programs where \mycroft or \sherrloc
encountered an unsupported language feature or timed out after one
minute, or where \toolname failed to produce a witness.
%
We discard all such programs in our evaluation to level the playing
field, around 15\% for each tool, leaving us with a benchmark set of
1,569 programs.

\begin{figure}[t]
\includegraphics[width=0.7\linewidth]{blame.png}
\caption{Accuracy of type error localization. \toolname's witness-based
  predictions outperform \ocaml by 22 points, and are competitive
  with the state-of-the-art tools \mycroft and \sherrloc.}
\label{fig:results-blame}
\end{figure}
